Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-28 thesis/chapters/ch_chapter4.tex
updates to ch4

>>>>

In Chapter~\ref{ch:chapter3} we investigate the metal enrichment distributions in the ISM as characterized by the metal fraction PDFs (see Figure~\ref{ch3:fig:log-normal} and Figure~\ref{ch3:fig:phase-statistics}). We find that this PDF is generally well described as log-normal with a power law tail towards high metal fractions, and characterize its mean, median, interquartile range (IQR), interdecile range (IDR), and the difference between the mean and median (as a measure of skew) of each distribution. In general, we find that elements released in AGB-wind events are less well-mixed than elements released in SNe, as indicated by the relative size of the IQR, IDR, and mean-median difference between the two types of elements. However, these distributions arise from the contribution of many individual enrichment events across multiple sources over long periods of time. It is unclear how metals from a \textit{single} enrichment event are distributed across a galaxy over time, and how the energy associated with the event affects the homogeneity of its distribution.

To frame this analysis, lets first examine what processes affect the metal mass fraction PDF. The mean metal mass fraction for a collection of gas is simply the total metal mass divided by the total gas mass. For a collection of gas elements, the mean metal mass fraction is defined as $Z_{\rm gas} = \frac{ \Sigma Z_{\rm i}M_{\rm gas,i}}{\Sigma M_{\rm gas,i}}$, where $M_{\rm gas,i}$ is the mass of the i$^{\rm th}$ homogeneous blob of gas, and $Z_{i}$ its metal mass fraction. A completely homogenous ISM would have a $\delta$ function metal mass fraction PDF at the mean metal fraction, or $p(Z) = \delta(Z_{\rm gas})$. By definition, a completely homogeneous distribution will have
